Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-12-06 paper/main.tex
K to S clean up

We also introduce an analogous category $\mathcal{\gbase}$ that encapsulates the topology of the space in which the graphic is displayed, for example whether it is a 2D screen or a 3D printer.

@@

The data space \dbase\ is a deformation retract of the graphic topology \gbase\
\begin{equation}
  \label{eq:artist:gbase}
  \gbase = \dbase \times I^{\text{dim}(display)-\text{dim}(\dbase)} 
\end{equation}
meaning that regions in \gbase\ collapse to points in \dbase\ such that the relative positions of the points are preserved \cite{nlab:deformation_retract}. The dimensionality of the data \dbase\ is expanded to match the dimensionality of the graphic display space by multiplying the data base space \dbase\ by intervals I.

@@

For example, as illustrated in \autoref{fig:artist:gbase}, the display space is a 2D screen and the data space is a 1D line \dbase. For that line to have any thickness, it must be rendered as a band. This means the region $(\dbasepoint, \alpha)\vert_{\alpha \in I} \subset \gbase$ maps to the corresponding point $\dbasepoint \in \dbase$.

@@

\begin{equation}
  \label{eq:artist:artist_sheaf}
  \begin{tikzcd}[column sep=tiny, row sep=huge]
    {\cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}}&  & 
    \textcolor{set}{\big\{}\gsectionc:\opensetgc\rightarrow \gtotalc\restriction_{\opensetgc} 
    \bigm{\vert} \vartist(\dsectionc) = \gsectionc \textcolor{set} \;, \dsectionc \in \sheafc(\dtotalc){\big\}} 
    \arrow[ll, "\textcolor{set}{\mathlarger{\mathlarger{\supset}}}" description, hook', color=white] \\ &  & \\
    \opensetgc \arrow[uu, "\sheafc(\gtotalc)", color=sheaf] \arrow[rruu, "\vartistc(\sheafc(\dtotalc))\coloneqq \sheafc_{\vartistc}(\gtotalc)" description, dashed, color=sheaf] &  & 
    \end{tikzcd}
\end{equation}

>>>>

We also introduce an analogous category $\mathcal{\gbase}$ that encapsulates the topology of the graphic, which is the topology of the rendering in the display space; for example, this rendering can be a 2D or volumetric image or a 3D print.

@@

The data space \dbase\ is a deformation retract of the graphic topology \gbase\meaning that regions in \gbase\ collapse to points in \dbase\ such that the relative positions of the points are preserved \cite{nlab:deformation_retract}. One method of constructing the graphic space is by expanding the dimensionality of the data \dbase\ to match the spatial dimensionality of the rendering by multiplying the data space by  intervals $I$.

@@

For example, as illustrated in \autoref{fig:artist:gbase}, the display space is a 2D screen and the data space is a 1D line \dbase. For that line to have any thickness, it must be rendered as a ban. One method of obtaining this graphic continuity while preserving the constraint that it is a deformation retract is by multiplying the base space \dbase\ by an interval $I=\[0,1\]$ such that $\gbase = \dbase \times I^{1}$. This construction ensures that every region $(\dbasepoint, \alpha)\vert_{\alpha \in I} \subset \gbase$ maps to a  corresponding point $\dbasepoint \in \dbase$.

@@

\begin{equation}
  \label{eq:artist:artist_sheaf}
  \begin{tikzcd}[column sep=tiny, row sep=huge]
    {\cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}}&  & 
    \textcolor{set}{\big\{}\gsectionc:\opensetgc\rightarrow \gtotalc\restriction_{\opensetgc} 
    \bigm{\vert} \vartist(\dsectionc) = \gsectionc \;, \dsectionc \in \sheafc(\dtotalc)\textcolor{set}{\big\}} 
    \arrow[ll, "\textcolor{set}{\mathlarger{\mathlarger{\supset}}}" description, hook', color=white] \\ &  & \\
    \opensetgc \arrow[uu, "\sheafc(\gtotalc)", color=sheaf] \arrow[rruu, "\vartistc(\sheafc(\dtotalc))\coloneqq \sheafc_{\vartistc}(\gtotalc)" description, dashed, color=sheaf] &  & 
    \end{tikzcd}
\end{equation}
